### 2019-03-06 paper/sex_selection_spacing-ver2.tex
Minor edit of intro paragraph

Birth spacing has long served as a measure of son preference, with strong
son preference typically associated with shorter birth intervals the
fewer sons a family has \citep{ben-porath76b,Leung1988}.
However, the introduction of prenatal sex determination has the potential to
fundamentally change the relationship between son preference and birth spacing.
The stronger the son preference, the more likely couples are to resort to sex-selective 
abortions, and each abortion automatically increases the interval between births by six 
months to a year.%
\footnote{
The increase consists of three parts.
First, starting from the time of the abortion, the uterus needs at 
least two menstrual cycles to recover;  otherwise, the likelihood 
of spontaneous abortion increases substantially \citep{zhou00b}.
The second part is the waiting time to conception, which is between 
one and six months \citep{Wang2003}.
Finally, sex determination tests are reliable only from three months 
of gestation onwards.
}
Longer birth intervals may, therefore, no longer be an indication of declining son
preference, but could instead come about precisely because strong son preference makes
couples more likely to use sex selection.
% To further complicate matters, families with son preference who---for one reason or 
% another---do not use prenatal sex selection may continue to have shorter birth spacing 
% than those with a lower preference for sons.

>>>>

Birth spacing has long served as a measure of son preference, with strong
son preference typically associated with shorter birth intervals the
fewer sons a family has \citep{ben-porath76b,Leung1988}.
However, the introduction of prenatal sex determination has the potential to
fundamentally change the relationship between son preference and birth spacing.
The stronger the son preference, the more likely couples are to resort to sex-selective 
abortions, and each abortion automatically increases the interval between births by six 
months to a year.%
\footnote{
The increase consists of three parts.
First, starting from the time of the abortion, the uterus needs at 
least two menstrual cycles to recover;  otherwise, the likelihood 
of spontaneous abortion increases substantially \citep{zhou00b}.
The second part is the waiting time to conception, which is between 
one and six months \citep{Wang2003}.
Finally, sex determination tests are reliable only from three months 
of gestation onwards.
}
Longer birth intervals may, therefore, cease to be an indication of declining son
preference, but could instead come about precisely because strong son preference makes
couples more likely to use sex selection.
% To further complicate matters, families with son preference who---for one reason or 
% another---do not use prenatal sex selection may continue to have shorter birth spacing 
% than those with a lower preference for sons.
